\documentclass[12pt]{article}

\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}

\hypersetup{
colorlinks=true,
linkcolor=black
}
\numberwithin{equation}{section}

\title{The Draft of MrHeer}
\author{MrHeer}
\date{\today}
 
\begin{document}

\begin{titlepage}
    \maketitle
    \thispagestyle{empty}
\end{titlepage}

\begin{center}
    \tableofcontents
\end{center}
\pagenumbering{roman}

\newpage
\pagenumbering{arabic}
\setcounter{page}{1}

\section{Throwing eggs from a building}
\subsection*{Question}
Suppose that you have an $N$-story building and
plenty of eggs. Suppose also that an egg is broken if it is thrown off floor $F$ or higher,
and unhurt otherwise. First, devise a strategy to determine the value of $F$ such that the
number of broken eggs is $\sim$$\lg{N}$ when using $\sim$$\lg{N}$ throws, then find a way to reduce the
cost to $\sim$$2\lg{F}$.
\subsection*{Answer}
$\sim$$\lg{N}$: start at the middle, always cut search space in half $\rightarrow$ binary search.\\
$\sim$$2\lg{F}$: start at 1, next 2, 4, 8 (i.e., $2^i$), once the egg breaks after ($\sim$$\lg{F}$ steps)
do binary search in the smaller search space (range $<$ $F$ and hence number of searches $<$ $\sim$$\lg{F}$)
$\rightarrow$ exponential search.
\[2^{\lceil \lg{F} \rceil - 1} < F \leqslant 2^{\lceil \lg{F} \rceil}\]
\[range = 2^{\lceil \lg{F} \rceil} - 2^{\lceil \lg{F} \rceil - 1}
= 2^{\lceil \lg{F} \rceil - 1} < 2^{\lg{F}} = F\]
\[range < F\]

\newpage
\section{Throwing two eggs from a building}
\subsection*{Question}
Consider the previous question, but now
suppose you only have two eggs, and your cost model is the number of throws. Devise
a strategy to determine $F$ such that the number of throws is at most $2\sqrt{N}$, then find a
way to reduce the cost to $\sim$$c\sqrt{F}$. This is analogous to a situation where search hits (egg
intact) are much cheaper than misses (egg broken).
\subsection*{Answer}
Let us make our first attempt on $k$'th floor.
If it breaks, we try remaining $(k-1)$ floors one by one. 
So in worst case, we make $k$ trials.
If it doesn’t break, we jump $(k-1)$ floors (Because we have
already made one attempt and we don't want to go beyond 
$k$ attempts. Therefore $(k-1)$ attempts are available),
Next floor we try is floor $k + (k-1)$
Similarly, if this drop does not break, next need to jump 
up to floor $k + (k-1) + (k-2)$, then $k + (k-1) + (k-2) + (k-3)$
and so on.
Since the last floor to be tried is $F$'th floor, sum of
series should be $F$ for optimal value of $k$.
\[k + (k-1) + (k-2) + (k-3) + \cdots + 1 \geqslant F\]
\[\frac{k(k+1)}{2} \geqslant F\]
\[k \geqslant \frac{\sqrt{8F+1}-1}{2}\]
\[k_{min} = \lceil \frac{\sqrt{8F+1}-1}{2} \rceil \sim \sqrt{2F}\] 
\subsubsection*{Official solution}
Solution to Part 1: To achieve $2\sqrt{N}$, drop eggs at floors $\sqrt{N}$,
$2*\sqrt{N}$, $3*\sqrt{N}$, ..., $\sqrt{N}\sqrt{N}$. (For simplicity, we assume
here that $\sqrt{N}$ is an integer.) Let assume that the egg broke at level
$k\sqrt{N}$. With the second egg you should then perform a linear search in the
interval $(k-1)\sqrt{N}$ to $k\sqrt{N}$. In total you will be able to find the
floor $F$ in at most $2\sqrt{N}$ trials.\\
Hint for Part 2: $1 + 2 + 3 + \cdots + k \sim \frac{1}{2}k^2 \geqslant F$. 

\newpage
\section{3-collinearity}
\subsection*{Question}
Suppose that you have an algorithm that takes as input $N$ distinct
points in the plane and can return the number of triples that fall on the same line.
Show that you can use this algorithm to solve the 3-sum problem. Strong hint: Use
algebra to show that $(a, a^3)$, $(b, b^3)$, and $(c, c^3)$ are collinear if and only if $a + b + c = 0$.
\subsection*{Answer}
\begin{proof}
    $(a, a^3)$, $(b, b^3)$, and $(c, c^3)$ are collinear if and only if $a + b + c = 0$: \\
    We use a formulation of collinearity which equates gradients (assuming our points are distinct) 
    \[\frac{y_2-y_1}{x_2-x_1}=\frac{y_3-y_1}{x_3-x_1}\]
    This becomes
    \[\frac{b^3-a^3}{b-a}=\frac{c^3-a^3}{c-a}\]
    which leaves us with
    \[b^2+ab+a^2=c^2+ac+a^2\]
    so that
    \[b^2-c^2=a(c-b)\]
    $c \neq b$ so we have $a=-(b+c)$
    \[a+b+c=0\]
\end{proof}

\end{document}
